\chapter{Cofibrant non-singular simplicial sets}
\label{ch:sixth}

Usually, one wants to know more about a model structure than its existence. Otherwise it may not be of much use. So far we at least know that the model category of non-singular simplicial sets is cofibrantly generated and proper.

For example, one of the first questions concerning a model category is what its cofibrant objects are. As the construction that establishes \cref{thm:main_homotopy_theory} is borrowed from Thomason \cite{Th80}, it makes sense to learn what we can from his article. He proved that any cofibrant small category is a poset.

When looking at (\ref{eq:diagram_of_adjunctions}), a semi-analogous statement to Thomason's result seems to be the following.
\begin{conjecture}\label{conj:cofibrant_nonsing_simp_set}
Any cofibrant non-singular simplicial set that is (isomorphic to) the nerve of a category is in fact (isomorphic to) the nerve of a poset.
\end{conjecture}
\noindent We will try to justify calling this statement a conjecture during the span of this chapter.

G. Raptis pointed out to the author that \cref{conj:cofibrant_nonsing_simp_set} is false without the assumption that the cofibrant non-singular simplicial set is isomorphic to the nerve of a category.

In \cref{sec:simplexcat}, we present constructions of various simplex categories. We also make basic comparisons. The reason we do this is that the Barratt nerve is defined in terms of the most drastically formed simplex category. We recommend that the reader skips or skims through this section, and then returns to it if needed.

In \cref{sec:evidence}, we explain how \cref{thm:main_opt_triang} is evidence for \cref{conj:cofibrant_nonsing_simp_set}. Furthermore, we indicate why a study of simplex categories might be useful in the work of characterizing the cofibrant non-singular simplicial sets.

In \cref{sec:justification}, we explain why one could hope for \cref{conj:cofibrant_nonsing_simp_set} by considering the first few stages of building a $DSd^2(I)$-cell complex.

In \cref{sec:possible}, we discuss some relevant examples. For instance, we display obstructions of statements that one could make concerning the cofibrant non-singular simplicial sets. We also display a few more ingredients in a possible proof of \cref{conj:cofibrant_nonsing_simp_set} or other statements that one could make.




\input{chapters/cofibrantobj/simplexcat}
\input{chapters/cofibrantobj/evidence}
\input{chapters/cofibrantobj/justification}
\input{chapters/cofibrantobj/possible}




